### 2014-04-12 docs/seminar/casestudy.tex
paper draft

\section{Case Study}
\label{sec:casestudy}
The data flow of expert searching is depicted in Figure \ref{fig:architecture}. The client submits a document and searches for translators with a specific target language. Based on the query document, the framework figures out the offered price, delivery time, proficiency of translators as well as the number of cooperation times related to each translator. The ranking system processes the calculated values and the offers the most related translators to the client.

As it is shown in Figure \ref{fig:architecture}, the essential components of the framework are \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiler}.

\begin{figure*}[h]
\begin{center}
\includegraphics[scale=0.8]{figures/dataflow.jpg}
\caption{System Data Flow
\label{fig:architecture}}
\end{center}
\end{figure*}

The \textit{Profiler} is responsible for accumulating translators' professional information,  offered price and translation duration per word. The \textit{Ranking} system uses Learning to Rank techniques to return the most related translators to the client. The training data is provided by a group of annotators who are familiar with the business of company using an evaluation system. The evaluation system suggests three translators and the annotators rate them by comparing between their factors. In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture. Applied learning to rank methods and results are described in Section \ref{sec:apply}. The \textit{Proficiency Estimator} system stores the previous-translated documents in the cloud and indexes them using Lucene. The similarity between query and indexed documents is used as a basis for the estimation of translator's proficiency. The proficiency value is compared by aggregating the similarity scores. The applied aggregation function is described in Section \ref{sec:apply}. The \textit{Scheduler} system figures out the delivery time based on timetable of translators. The scheduler builds a special data structure to calculate the delivery time in a reasonable response time. The details of the process are out of scope of the paper.

Beside the translator, a proofreader selected by the client revises the final translation. As well as reviewing, the proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language). The assessment is defined as a value between $1$ (very bad) and $5$ (perfect). We use these assessments to evaluate and compare aggregation algorithms for translator's proficiency.

>>>>

\section{Case Study}
\label{sec:casestudy}
Essential components of the platform as well as the work-flow of searching for the translators are depicted in Figure \ref{fig:architecture}. The platform consist of four main components: \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiles}.

\begin{figure*}[h]
\begin{center}
\includegraphics[scale=0.8]{figures/dataflow.png}
\caption{Translator-Expert Search Work Flow
\label{fig:architecture}}
\end{center}
\end{figure*}

The \textit{Profiles} stores translator profile information i.e. source and target languages, offered price and translation duration per word. The \textit{Scheduler} system figures out the delivery time based on timetable of translators. The scheduler builds an efficient data structure to calculate the delivery time in a reasonable response time. The details of the process are out of scope of the paper. The \textit{Proficiency Estimator} system stores the previous-translated documents and indexes them using Lucene. The similarity between query and indexed documents is used as a basis for the estimation of translator's proficiency. In fact, the proficiency value is achieved by aggregating the documents similarity scores. The applied aggregation function is described in Section\ref{sec:apply}. At last, the \textit{Ranking} system uses all the data provided in the previous steps to create the ranking model. The \textit{Ranking} system applies Learning to Rank techniques to return the most related translators to the client. The training data is provided by a group of annotators who are familiar with the business of company using an evaluation system. The evaluation system suggests three translators and the annotators rate them by comparing between their factors. In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture. Applied learning to rank methods and results are described in Section\ref{sec:apply}.

The client submits a document and searches for translators with a specific target language. Based on the query document, the framework figures out the offered price, delivery time, proficiency of translators as well as the number of cooperation times related to each translator. The ranking system processes the calculated values and offers the most related translators to the client.

Beside the mentioned work-flow after finishing the translation, another expert called proofreader revises the translation. The proofreader is selected by the client and guarantees the quality of the final translation. As well as revising, the proofreader assesses the quality of translator's task from different points of view (grammar, style, accuracy, content and language). The assessment value can be from $1$ (very bad) to $5$ (perfect). As it is described in Section\ref{sec:apply}, we use these assessments to evaluate and compare aggregation algorithms.

### 2014-04-12 docs/seminar/evaluation.tex
paper draft

\subsection{Aggregation Functions}
In order to compare different aggregation functions, similar to \citet{agg-gp2} three algorithms are selected. $GP2$ as well as $Top1$ and $Top5$ which are two common forms of $TopN$ aggregation algorithm. $TopN$ refers to algorithm that summarizes the $N$ top documents (i.e. $Top1$ only using the top associated document to rank the candidates).

Feedbacks of proof-readers after every translation are used as a basis for evaluating the algorithms. Since feedbacks are a measure for quality of translation, the more similar the ranking of algorithms to feedbacks are the better it is.

By calculating the value of each mentioned algorithm on all finished translations, we achieve three lists of translations each annotated with an additional aggregation value field. In the next step, in order to compare the algorithms, we test the correlation of each list with the proof-readers' feedbacks.

@@

As it is usual in many cases, the coefficient value of Spearman is slightly higher than Kendall's. The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers. Regarding to P-Value of significance test shown in Table \ref{table:correlation}, a meaningful relation between GP2 and feedbacks can be considered. Top1 which has the worst values in the table shows a meaningless and near random correlation though.

@@

\subsection{Learning To Rank}
In order to accumulate data required for ranking model, we conduct a survey filled by eight human annotators. The questions of survey represent three translators each with four criteria (price, delivery time, proficiency and number of cooperation times). The annotators rate the questions from one to three based on \textit{Total Order} strategy. The accumulated data consists of $400$ annotated list and overall $1200$ records.

@@

The result is shown in Table \ref{table:l2rresult}.  Figure \ref{fig:l2rdiagram} depicts the corresponding data in diagrams. As it is shown, random values define a base line for comparison the goodness of methods. Among the applied methods, Linear Regression and LambdaMART tend to have better results. Furthermore, tracing NDCG and ERR diagrams shows a considerable similarity in behavior of both evaluation methods regarding to the data.

In addition to comparing the methods, features comparison can be an interesting point. Table \ref{table:l2rcoefficient} shows the coefficients of features, calculated in Linear Regression model. The coefficient value is a measure for understanding the importance of each feature in comparison to the others.

>>>>

\subsection{Aggregation Functions}
Translator's proficiency is one of the attributes used for creating the ranking model. In order to achieve the value, we aggregate the similarity values of the previous translated documents with the query document. Selecting the most appropriate aggregation function is the objective of the current section.

Similar to \citet{agg-gp2}, we compare three aggregation algorithms: $GP2$, $Top5$ and $Top1$. $Top1$ and $Top5$ are two common forms of $TopN$ aggregation algorithm which refers to algorithm that summarizes the $N$ top documents (i.e. $Top1$ only using the top associated document to rank the candidates).

In order to evaluate aggregation functions results, we use the assessment of the proof-readers after every translation as the basis for the comparison. **the reason**. Therefore, the more similar the results of the algorithm to the assessments are the better the algorithm is.

By calculating the value of each mentioned algorithm on all finished translations, we achieve three lists of translations each annotated with an additional aggregation value field. In the next step, in order to compare the algorithms, we test the correlation of each list with the list of translations annotated with proof-readers' assessments.

@@

As it is usual in many cases, the coefficient value of Spearman is slightly higher than Kendall's. The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers. Regarding to P-Value of significance test shown in Table\ref{table:correlation}, a meaningful relation between GP2 and feedbacks can be considered. Top1 which has the worst values in the table shows a meaningless and near random correlation though.

@@

\subsection{Learning To Rank}
In order to accumulate data required for ranking model, we conduct a survey filled by eight human annotators. The questions of survey represent three translators each with four criteria (price, delivery time, proficiency and number of cooperation times). As it is mentioned before, in order to prevent bias in results, the name and the picture of the translators are hidden from the annotators. The annotators rate the questions from one to three based on \textit{Total Order} strategy. The accumulated data consists of $400$ annotated list and overall $1200$ records.

@@

The result is shown in Table\ref{table:l2rresult}.  Figure\ref{fig:l2rdiagram} depicts the corresponding data in diagrams. As it is shown, random values define a base line for comparison the goodness of methods. Among the applied methods, Linear Regression and LambdaMART tend to have better results. Furthermore, tracing NDCG and ERR diagrams shows a considerable similarity in behavior of both evaluation methods regarding to the data.

In addition to comparing the methods, features comparison can be an interesting point. Table\ref{table:l2rcoefficient} shows the coefficients of features, calculated in Linear Regression model. The coefficient value is a measure for understanding the importance of each feature in comparison to the others.

### 2014-04-12 docs/seminar/introduction.tex
paper draft

With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR such as entity retrieval and expertise retrieval \citep{er-sparse}  and not just traditional document retrieval. The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.

Two principal approaches are proposed by \citet{trec2005} based on probabilistic language modeling techniques. They were formalized as so-called candidate models and document models. The candidate-based approach, also referred to as profile-based method, builds a textual representation of candidate experts and then ranks them based on the query. The document models first find documents relevant to the topic and then locate the experts associated with these documents \citep{er}.

@@

This paper addresses the problem of searching translators as experts. We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on the practical implementation of the platform. In contrast to common expert retrieval systems, we include significant factors of searching a translator (like price and delivery time) in the study as well as the relevance of the documents to the query document. We have applied Learning to Rank in a candidate-based approach. Additionally, different aggregation algorithms related to documents of translators have been studied.

The remaining of the paper is organized as follows. In Section \ref{sec:casestudy}, the Translator-Expert Retrieval framework is described in detail. Then, Section \ref{sec:methods} explains methods used in the study. In Section \ref{sec:apply}, we report the result of applied methods on the framework. Finally, we conclude the study in Section \ref{sec:conclusion}.

>>>>

With the development of information retrieval (IR) techniques, many research efforts go beyond traditional document retrieval and address high-level IR such as entity retrieval and expertise retrieval \citep{er-sparse}. The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, following by rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.

\citet{trec2005} propose two principal approaches  in the expertise retrieval area based on probabilistic language modeling techniques. They were formalized as so-called \textit{candidate models} and \textit{document models}. The candidate-based approach, also referred to as profile-based method, builds a textual representation of candidate experts and then ranks them based on the query. The document models first find documents relevant to the topic and then locate the experts associated with these documents \citep{er}.

@@

This paper addresses the problem of searching translators as experts. We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on the practical implementation of the platform. In contrast to common expert retrieval systems, we include significant factors of searching a translator (like price and delivery time) in the study as well as the relevance of the documents to the query document. We have applied Learning to Rank in a candidate-based approach. Additionally, different aggregation algorithms related to documents of translators have been studied and compared.

The remaining of the paper is organized as follows. In Section\ref{sec:casestudy}, the Translator-Expert Retrieval framework is described in detail. Then, Section\ref{sec:methods} explains methods used in the study. In Section\ref{sec:apply}, we report the result of applied methods on the framework. Finally, we conclude the study in Section\ref{sec:conclusion}.
